---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  warning    = FALSE,
  message    = FALSE,
  comment    = "#>",
  fig.path   = "figs/",
  fig.retina = 3
)

library(fontawesome)
```

# formr4conjoint

<!-- badges: start -->
[![CC BY-NC-SA 4.0][cc-by-nc-sa-shield]][cc-by-nc-sa]

[cc-by-nc-sa]: http://creativecommons.org/licenses/by-nc-sa/4.0/
[cc-by-nc-sa-image]: https://licensebuttons.net/l/by-nc-sa/4.0/88x31.png
[cc-by-nc-sa-shield]: https://img.shields.io/badge/License-CC%20BY--NC--SA%204.0-lightgrey.svg
<!-- badges: end -->

[formr.org](https://formr.org/) is a flexible platform for making surveys using `r fa("r-project")`. This repo contains files for designing and implementing a demo conjoint survey with formr about people's preferences for apples with three attributes: `type`, `price`, and `freshness`.

See [this post](https://www.jhelvy.com/posts/2021-09-18-choice-based-conjoint-surveys-in-r-with-formr/) for more details about the demo.

You can view the live demo survey [here](https://appleconjoint.formr.org/)

## Packages

If you want to run the code in the `survey` folder, you will need to install the following packages:

```{r, eval=FALSE}
install.packages(c("remotes", "tidyverse", "jsonlite"))
remotes::install_github("jhelvy/conjointTools")
```

## Author and License Information

- Author: *John Paul Helveston* https://www.jhelvy.com/
- Date First Written: *Monday, August 12, 2019*
- This work is licensed under a
[Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License][cc-by-nc-sa].

[![CC BY-NC-SA 4.0][cc-by-nc-sa-image]][cc-by-nc-sa]
