---
output: html_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  warning    = FALSE,
  message    = FALSE,
  comment    = "#>",
  fig.path   = "man/figures/",
  fig.retina = 3
)
```

```{r, include=FALSE}
# Read in the choice questions
library(tidyverse)
survey <- read_csv("https://raw.githubusercontent.com/jhelvy/formr4conjoint/master/survey/choice_questions.csv")

# Define the respondent ID
respondentID <- sample(survey$respID, 1)

# Create the subset of rows for that respondent ID
df <- survey %>%
    filter(respID == respondentID) %>%
    mutate(image = paste0("https://raw.githubusercontent.com/jhelvy/formr4conjoint/master/survey/images/", image))

# Convert df to json
df_json <- jsonlite::toJSON(df)
```

# Great work!

Now let's begin the choice tasks. You will be asked 8 questions in total.

---

(1 of 8) If these were your only options, which would you choose?

```{r, include=FALSE}
library(dplyr)
temp <- jsonlite::fromJSON(df_json)
alt1 <- temp %>% filter(qID == 1, altID == 1)
alt2 <- temp %>% filter(qID == 1, altID == 2)
alt3 <- temp %>% filter(qID == 1, altID == 3)
```

**Option 1**

![](`r alt1$image`){width=100}

**Type**: `r alt1$type`
**Price**: $ `r alt1$price` / lb
**Freshness**: `r alt1$freshness`

**Option 2**

![](`r alt2$image`){width=100}

**Type**: `r alt2$type`
**Price**: $ `r alt2$price` / lb
**Freshness**: `r alt2$freshness`

**Option 3**

![](`r alt3$image`){width=100}

**Type**: `r alt3$type`
**Price**: $ `r alt3$price` / lb
**Freshness**: `r alt3$freshness`
